Deploying databases across multiple regions has become the de facto choice for cloud-native applications that desire high availability, strong scalability, and efficient service localization. However, supporting serializable transactions in such databases presents a significant challenge. Coordinating cross-region transactions (CRTs) is inherently slow due to the extensive geographic distances. Even a few slow transactions can significantly degrade the performance of the entire system. 
% This poor performance significantly limits the practicality of multi-region databases. 
Despite various proposals introduced to optimize the performance by either eliminating CRTs or minimizing the cost of cross-region coordination, CRTs remain crucial for general workloads, with their costs still being dozens of times higher than those of intra-region transactions (IRTs).
% These databases typically partition data into shards 

This paper contends that existing serializable consistency models are not well-designed for multi-region deployments. The root cause is the strong heterogeneity in deployments: certain transactions (e.g., CRTs) experience significantly higher committing latency than others.
% [TODO: add a sentence]
To address this, we propose a new layered consistency model specifically tailored for multi-region deployments: region-linearizable serializability (RLS). Specifically, RLS ensures strict serializability (i.e., linearizability) for IRTs from the same region and provides regular serializability for CRTs.

To demonstrate the efficiency and applicability of our new consistency model (i.e., RLS), we design, implement, and evaluate variations of two representative database systems: Spanner and CockroachDB. Our evaluation demonstrates that these variations can significantly enhance performance (e.g., $4.5\times$ throughput for Spanner on average) or provide better functionality without performance degradation (e.g., more consistency guarantees for CockroachDB). 